Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-03 Documents/M1/realizableFermionicM1/sections/appendix.tex
Some adjustments to text in appendix

We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step for positivity).  
The scheme chosen by random sampling of the parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.  
For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
This scheme is also GSA; $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

@@

A second-order accurate, positivity-preserving, diffusion accurate IMEX scheme was given in \cite{mcclareen_2008}.  
We refer to this scheme as IMEX PC2.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
A common choice of this scheme is $c_{sch} = 0.3$.

@@

A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

@@

A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{pareschiRusso_2005}.  
We refer to this scheme as IMEX SSP2332.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 1/2, \nonumber \\
  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
  a_{11} &= 1/4, \nonumber \\
  a_{22} &= 1/4, \nonumber \\
  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

>>>>

We have found another second-order accurate, positivity-preserving IMEX scheme of type $A$, which we refer to as IMEX PA2+.  
This scheme allows for has a larger $c_{sch}$ than IMEX PA2 (i.e., a larger time step while still maintaining positivity).  
The scheme chosen from random sampling of the IMEX parameter space, and was the scheme with the largest $c_{sch}$ that satisfied both the order conditions for second order accuracy and possessed the positivity-preserving property.  
For IMEX PA2+, ($c_{sch} = 0.895041066934$). 
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
This scheme is also GSA; $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

@@

Another positivity-preserving IMEX scheme was given in \cite{mcclareen_2008} (referred to as a semi-implicit predictor-corrector method in \cite{mcclareen_2008}).  
This scheme can be written in the double Butcher tableau form, and we refer to this scheme as IMEX PC2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
A common choice of this scheme is $c_{sch} = 0.3$.

@@

We compare the performance of the positivity-preserving IMEX schemes with two other, non-positive, schemes.  
The first one is the second-order accurate IMEX scheme given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

@@

The second scheme we use for comparison is the second-order accurate IMEX scheme given in \cite{pareschiRusso_2005}.  
We refer to this scheme as IMEX SSP2332.  
The non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 1/2, \nonumber \\
  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
  a_{11} &= 1/4, \nonumber \\
  a_{22} &= 1/4, \nonumber \\
  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...
